Results (Barcelona)

### 2022-01-20 docs/06_results-bcn.Rmd
Model comparisons with simpler models

waics %>% 
	map("estimates") %>% 
	map(function(x) as.data.frame(x) %>% rownames_to_column("variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	as_raw_html()

@@

draws_intercept <- draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5,
		color = "#FF6F00FF",
		fill = "#FF6F00FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1))

draws_predictors <- draws %>% 
	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#C71000FF", 
		fill = "#C71000FF") +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))

draws_time <- draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	ggplot(aes(.value, .variable_name)) +
	facet_wrap(~type, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	# stat_slab(
	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
	# 	size = 0.5, 
	# 	color = "#008EA0FF", 
	# 	fill = "#008EA0FF"
	# ) +
	stat_pointinterval(
		color = "#008EA0FF",
		fill = "#008EA0FF",
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent)

draws_sigma <- draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(aes(.value, .variable_name)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#8A4198FF", 
		fill = "#8A4198FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))

@@

corr_mat <- VarCorr(fit_total, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_total, summary = TRUE)$participant$cor)

@@

# correlations by item
corr_mat <- VarCorr(fit_total, summary = TRUE)$target$cor 
corr_names <- rownames(VarCorr(fit_total, summary = TRUE)$target$cor)

@@

m <- epred_draws(object = fit_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_total_center = ifelse(
			vocab_size_total_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

@@

m <- epred_draws(object = fit_total, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_total_center = ifelse(
			vocab_size_total_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

@@

m <- emmeans(fit_total, ~trial_type | lp, epred = TRUE)

@@

draws <- gather_draws(fit_l1, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)

@@

draws_intercept <- draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5,
		color = "#FF6F00FF",
		fill = "#FF6F00FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1))

draws_predictors <- draws %>% 
	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#C71000FF", 
		fill = "#C71000FF") +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))

draws_time <- draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	ggplot(aes(.value, .variable_name)) +
	facet_wrap(~type, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	# stat_slab(
	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
	# 	size = 0.5, 
	# 	color = "#008EA0FF", 
	# 	fill = "#008EA0FF"
	# ) +
	stat_pointinterval(
		color = "#008EA0FF",
		fill = "#008EA0FF",
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent)

draws_sigma <- draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(aes(.value, .variable_name)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#8A4198FF", 
		fill = "#8A4198FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))

@@

corr_mat <- VarCorr(fit_l1, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_l1, summary = TRUE)$participant$cor)

@@

# correlations by item
corr_mat <- VarCorr(fit_l1, summary = TRUE)$target$cor 
corr_names <- rownames(VarCorr(fit_l1, summary = TRUE)$target$cor)

@@

m <- epred_draws(object = fit_l1, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_l1_center = ifelse(
			vocab_size_l1_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

@@

@@

m <- emmeans(fit_l1, ~trial_type | lp, epred = TRUE)

>>>>

model_comparison <- waics_l1 %>% 
	map("estimates") %>% 
	map(function(x) as.data.frame(x) %>% rownames_to_column("variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	mutate(model = str_replace_all(model, c("fit_l1_4" = "L1 vocab.", "fit_total_4" = "Total vocab."))) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	tab_style(
		cell_text(weight = "bold"),
		cells_column_spanners()
	) %>% 
	tab_style(
		cell_text(style = "italic"),
		cells_column_labels()
	)

gtsave(model_comparison, here("img", "model_comparison.png"))

as_raw_html(model_comparison)

@@

draws_intercept <- draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(0.95, 0.8, 0.5), labels = percent_format()))),
		size = 0.5,
		color = "#FF6F00FF",
		fill = "#FF6F00FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		axis.title.y = element_blank()
	)

draws_predictors <- draws %>% 
	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#C71000FF", 
		fill = "#C71000FF") +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
	theme(
		axis.title.y = element_blank()
	)

draws_time <- draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	ggplot(aes(.value, .variable_name)) +
	facet_wrap(~type, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	# stat_slab(
	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
	# 	size = 0.5, 
	# 	color = "#008EA0FF", 
	# 	fill = "#008EA0FF"
	# ) +
	stat_pointinterval(
		color = "#008EA0FF",
		fill = "#008EA0FF",
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent) +
	theme(
		axis.title.y = element_blank()
	)

draws_sigma <- draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(aes(.value, .variable_name)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#8A4198FF", 
		fill = "#8A4198FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0.92, 0.97)) +
	theme(
		axis.title.y = element_blank()
	)

@@

corr_mat <- VarCorr(fit_total_4, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$participant$cor)

@@

# correlations by item
corr_mat <- VarCorr(fit_total_4, summary = TRUE)$target$cor 
corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$target$cor)

@@

m <- epred_draws(object = fit_prior_l1_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_total_center = ifelse(
			vocab_size_total_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

@@

m <- epred_draws(object = fit_total_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_total_center = ifelse(
			vocab_size_total_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

@@

m <- emmeans(fit_total_4, ~trial_type | lp, epred = TRUE)

@@

draws <- gather_draws(fit_l1_4, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)

@@

draws_intercept <- draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5,
		color = "#FF6F00FF",
		fill = "#FF6F00FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		panel.grid.major.y = element_blank()
	)

ggsave(here("img", "posterior_intercept_l1.png"), draws_intercept, height = 2, width = 7)

draws_predictors <- draws %>% 
	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#C71000FF", 
		fill = "#C71000FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
	theme(
		panel.grid.major.y = element_blank()
	)

ggsave(here("img", "posterior_predictors_l1.png"), draws_predictors, height = 7, width = 7)

draws_time <- draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	ggplot(aes(.value, .variable_name)) +
	facet_wrap(~type, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	# stat_slab(
	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
	# 	size = 0.5, 
	# 	color = "#008EA0FF", 
	# 	fill = "#008EA0FF"
	# ) +
	stat_pointinterval(
		color = "#008EA0FF",
		fill = "#008EA0FF",
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent) +
	theme(
		panel.grid.major.y = element_blank(),
		panel.border = element_rect(fill = NA, colour = "grey"),
		axis.title = element_blank()
	)

ggsave(here("img", "posterior_poly_l1.png"), draws_time, height = 7, width = 9)

draws_sigma <- draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(aes(.value, .variable_name)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#8A4198FF", 
		fill = "#8A4198FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0.92, 0.96)) +
	theme(
		panel.grid.major.y = element_blank()
	)

ggsave(here("img", "posterior_sigma_l1.png"), draws_sigma, height = 2, width = 7)

@@

corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$participant$cor)

@@

# correlations by item
corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$target$cor 
corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$target$cor)

@@

m <- epred_draws(object = fit_l1_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_l1_center = ifelse(
			vocab_size_l1_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

@@

ggsave(here("img", "epreds_l1.pdf"), dpi = 1000)

@@

m <- emmeans(fit_l1_4, ~trial_type | lp, epred = TRUE)
